Insert the article title here

### 2018-08-17 writeup/manuscript.tex
changing abbrevs.

The study consists of three paradigms from the visual search literature in which large individual differences have been noted found\cite{nowakowska2017, irons-leber2016, kristjansson2014}. Example stimuli can be seen in Figure \ref{fig:exampleStimuli}. A brief overview of each paradigm is given below, with full details in \textit{supplementary materials}. The three tasks will be completed over two sessions, approximately one week apart. The split-half array search will be run in both sessions allowing us to measure test-retest reliability. The order in which participants completed the tasks was counter-balanced. There are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64.

@@

\subsubsection{Split-half Array Search}

@@

The ACVS was based on the task described in \cite{irons-leber2016}, Experiment 1. Each search display was composed of 54 small squares arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The same screen was used as in the Split-half Array Search, however, due to changes of screen resolution, the size of the squares changed. Participants, were sat $\approx$47cm from the screen. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable". Variable distractors change colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue. The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red.

@@

\subsubsection{Conjunction Foraging}

The foraging task was based on \cite{kristjansson2014} and \cite{johannesson2016}. Participants completed the feature foraging and conjunction foraging tasks on separate days, with the order counterbalanced (was it counterbalanced?).

In the feature foraging task, search displays contained 80 small circles, 20 red, 20 green, 20 blue  and 20 yellow. Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement. The location of item colours to grid locations was completely randomized.

For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles. Participants were asked to collect all of the targets within a trial by using the mouse to click on each target. Clicking on a target caused it to disappear from the display. If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun.

In the conjunction foraging task, search displays were composed of both circles and squares. For half of the participants, the shapes were red and green (equal numbers of red circles, red squares, green circles and green squares), and for the remaining participants the shapes were blue and yellow. Targets were defined by conjunctions of colour and shape (e.g., red squares and green circles, with red circles and green squares as distractors). The assignment of targets and distractors was assigned at random for each participant. The procedure was otherwise identical to the feature foraging task.

%% For the assignment of distractors and targets, we generated a two lists of random numbers (1-2 for easy search, and 1-4 for hard search). Pretty sure we did that because counterbalancing became very tricky once you accounted for that as well.

@@

\subsubsection{Split-half Array Search}
Our results are in line with the original split-half array study\cite{nowakowska2017}. Only trials with a correct target absent/present response were included in the analysis. Some participants performed exceptionally poorly and were removed from further analysis (full details given in the \textit{supplementary materials}). All reaction times were $\log_2$ transformed. In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on the heterogeneous (difficult) side of the stimuli, over all correct target absent trials. Previous work\cite{nowakowska2017} demonstrated a strong correlation between this metric (for $n=5$) and reaction times ($r=.53$).

@@

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
\caption{Each point represents a participant and the error-bars indicate 95\% confidence intervals. Correlation between the two sessions of the \textit{split-half} paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only). (d) Initial search strategy correlates with reaction times in both sessions. }
\label{fig:splithalf_summary}
\end{figure}

@@

\subsubsection{Adaptive Choice}

@@

\subsubsection{Conjunction Foraging}

@@

The results presented in Figure \ref{fig:all_the_cor} convincingly demonstrate that there are no strong correlations between the strategies by observers in split-half, adaptive choice and foraging visual search paradigms\footnote{More comparisons are presented in the \textit{supplementary materials.}}.

@@

While there is no indication of a relationship between strategies across the different paradigms, perhaps there is still a correlation between the reaction times due to some participants having higher levels of motivation than others, or stable speed-accuracy trade-offs between the different tasks. Differences relating to their information-processing speed and their ability to ignore distractors would also play in to such a correlation.However, as with search strategy, we again find all the correlations to be weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:all_the_cor}). None of these correlations are statistically significant ($p>0.05$). Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ means that this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

@@

Mention \cite{vogel2008}.
From \cite{proulx2011} - \textit{Vogel and colleagues have found that an individual’s ability to remember a greater number of items using working memory is related to a filtering capacity in visual search that suppresses attentional capture by distracting visual information [10,11,12]. Behavioural work in visual search has extended this research to
demonstrate that working memory correlates only with top-down
visual search performance where task relevance is crucial, but not
with  bottom-up  visual  search  tasks  where  salience  in  the
environment guides attention \cite{sobel2007}}

>>>>

The study consists of three paradigms from the visual search literature in which large individual differences have been noted found\cite{nowakowska2017, irons-leber2016, kristjansson2014}. Example stimuli can be seen in Figure \ref{fig:exampleStimuli}. A brief overview of each paradigm is given below, with full details in \textit{supplementary materials}. The three tasks will be completed over two sessions, approximately one week apart. The SHLS task will be run in both sessions allowing us to measure test-retest reliability. The order in which participants completed the tasks was counter-balanced. There are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64.

@@

\subsubsection{Split-half Line Segments}

@@

The ACVS was based on the task described in \cite{irons-leber2016}, Experiment 1. Each search display was composed of 54 small squares arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The same screen was used as in the Split-half Array Search, however, due to changes of screen resolution, the size of the squares changed. Participants, were sat $\approx 47$cm from the screen. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable". Variable distractors change colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for five trials (called a "red plateau"), then across a period of seven trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue. The variable distractor would then be blue for five trials (blue plateau), and then transition back from almost blue through magenta to almost red.

@@

\subsubsection{Mouse Click Foraging Task}

The foraging task (MCFT) was based on \cite{kristjansson2014} and \cite{johannesson2016} except that we used a mouse clicks to register responses rather than a touchpad.

In the feature foraging task, search displays contained 80 small circles, 20 red, 20 green, 20 blue  and 20 yellow. Stimuli were arranged in a $10 \times 8$ grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement. The location of item colours to grid locations was completely randomized.

For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles. Participants were asked to collect all of the targets within a trial by using the mouse to click on each target. Clicking on a target caused it to disappear from the display. If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun. In the conjunction foraging task, search displays were composed of both circles and squares. For half of the participants, the shapes were red and green (equal numbers of red circles, red squares, green circles and green squares), and for the remaining participants the shapes were blue and yellow. Targets were defined by conjunctions of colour and shape (e.g., red squares and green circles, with red circles and green squares as distractors). The assignment of targets and distractors was assigned at random for each participant. The procedure was otherwise identical to the feature foraging task.

@@

\subsubsection{Split-half Line Segments}

Our results are consistent with the original SHLS study\cite{nowakowska2017}. Only trials with a correct target absent/present response were included in the analysis. Some participants performed exceptionally poorly and were removed from further analysis\footnote{Full details given in the \textit{supplementary materials}}. All reaction times were $\log_2$ transformed. In order to characterise each participant's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on the heterogeneous (difficult) side of the stimuli, over all correct target absent trials. Previous work\cite{nowakowska2017} demonstrated a strong correlation between this metric (for $n=5$) and reaction times ($r=.93$).

@@

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
\caption{Each point represents a participant and the error-bars indicate 95\% confidence intervals. Correlation between the two sessions of the SHLS paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only). (d) Initial search strategy correlates with reaction times in both sessions. }
\label{fig:splithalf_summary}
\end{figure}

@@

@@

\subsubsection{Mouse Click Foraging Task}

@@

The results presented in Figure \ref{fig:all_the_cor} convincingly demonstrate that there are no strong correlations between any of the strategies chosen by observers in SHLS, ACVS and MCFT tasks \footnote{More comparisons are presented in the \textit{supplementary materials.}}. 
While there is no indication of a relationship between strategies across the different paradigms, perhaps there is still a correlation between the reaction times due to some participants having higher levels of motivation than others, or stable speed-accuracy trade-offs between the different tasks. Differences relating to their information-processing speed and their ability to ignore distractors would also play in to such a correlation. However, as with search strategy, we again find all the correlations to be weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:all_the_cor}). None of these correlations are statistically significant ($p>0.05$). Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ means that this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

@@

@@

Mention \cite{vogel2008}.
From \cite{proulx2011} - \textit{Vogel and colleagues have found that an individual's ability to remember a greater number of items using working memory is related to a filtering capacity in visual search that suppresses attentional capture by distracting visual information [10,11,12]. Behavioural work in visual search has extended this research to
demonstrate that working memory correlates only with top-down
visual search performance where task relevance is crucial, but not
with  bottom-up  visual  search  tasks  where  salience  in  the
environment guides attention \cite{sobel2007}}
